Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-02-12 ms.tex
Nothing wrong or outdated in Fisher matrix section
...but there are marginpar notes about what needs to be added.

Furthermore, the Fisher matrix in \Eref{eq:fisher-matrix} is block diagonal, which implies that estimation errors in the signal amplitude $\rho$ are uncorrelated with the phase $\gamma$ and time $\tau$. A sequence of two changes of variables lends some physical interpretation to the nature of the coupled estimation errors in $\gamma$ and $\tau$.

@@

\marginpar{This material still has the original, wrong Fishher matrix. Needs to be rewritten.}%
%
Because the \ac{CRLB} in \Eref{eq:cramer-rao} is diagonal, joint estimators of $(\rho_A, \rho_B, t_0)$ may exist for which the error in the estimation of the individual parameters is uncoupled up to second order. If the detector's noise is Gaussian, then the outputs of matched filters for $a(t)$ and $b(t)$ will themselves be Gaussian. This encourages us to make the approximation that the errors in $(\rho_A, \rho_B, t_0)$ by a matched\nobreakdashes-filter estimator are independent and Gaussian with variance equal to the \ac{CRLB}. A wrinkle is that $\mathcal{I}_{t_0,t_0}$ depends on the true values of $\rho_A$ and $\rho_B$. If we make the further leap of evaluating the \ac{CRLB} \emph{at the value of the estimators}, we can write
%
\begin{eqnarray}
\hat{\rho}_A - \rho_A \sim \mathcal{N}\, [0, 1] \\
\hat{\rho}_B - \rho_B \sim \mathcal{N}\, [0, 1] \\
\hat{t}_0 - t_0 \sim \mathcal{N} \left[0, \frac{1}{2 \pi f_\mathrm{rms} \sqrt{{\hat{\rho}_A}^2 + {\hat{\rho}_B}^2}}\right].
\end{eqnarray}

>>>>

\marginpar{Plot covariance ellipses and estimator samples for each change of variables; that would be a nice visual here.}%
%
Furthermore, the Fisher matrix in \Eref{eq:fisher-matrix} is block diagonal, which implies that estimation errors in the signal amplitude $\rho$ are uncorrelated with the phase $\gamma$ and time $\tau$. A sequence of two changes of variables lends some physical interpretation to the nature of the coupled estimation errors in $\gamma$ and $\tau$.

@@

\subsection{Noise model for point parameters}

\marginpar{Talk here about likelihood structure---the `gaussian on a cylinder' concept, why we would want to project out the phase error.}%
%
A wrinkle is that $\mathcal{I}_{\tau\tau}$ depends on the true values of $\rho_A$ and $\rho_B$. If we make the further leap of evaluating the \ac{CRLB} \emph{at the value of the estimators}, we can write
%
\begin{eqnarray}
    \hat{\rho} - \rho \sim \mathcal{N}\, [0, 1] \\
    \hat{\gamma} - \gamma \sim \mathcal{N}\, \left[0, \overline{\omega^2} / {\omega_\mathrm{rms}}^2\right] \\
    \hat{\tau} - \tau \sim \mathcal{N} \left[0, 1 / {\omega_\mathrm{rms}}^2\right].
\end{eqnarray}
